---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# networkedwebsitesdetector

The goal of networkedwebsitesdetector is to offer a structured approach for finding websites which have clear signs of common ownership or are otherwise related.

The package is mostly functional and should serve its purpose. However, it has not yet been fully tested. 

Basic documentation describing typical workflow is available on [`networkedwebsitesdetector`'s website](https://giocomai.github.io/networkedwebsitesdetector). Additional details, use cases, and examples of outputs will be added. 

## Installation

You can install the released version of `networkedwebsitesdetector` from [CRAN](https://CRAN.R-project.org) with:

``` r
remotes::install_github("giocomai/networkedwebsitesdetector")
```

As of this writing (`r Sys.Date()`), the package works with the development versions of both `tidyr` and `googledrive` and will result in errors with the current cran versions. This notice will be removed as soon as the current development version of both will make it to CRAN.

```{r eval=FALSE}
remotes::install_github("tidyverse/tidyr")
remotes::install_github("tidyverse/googledrive")
```

